Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
condensing threats

%\paragraph{Internal validity}
We use Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/}, a well known machine-learning tool,
to analyze our data.
Like all tools, Weka is prone to contain errors and/or bugs. 
Nonetheless, Weka is a well-known used, open source tool, and as such is likely
to be of relatively high quality, mitigating threats to internal validity.

 The scripts we have created to create the datasets and the 
 scripts to obtain the developer social data are publicly available 
 \footnote{https://goo.gl/CqTX44}.

%\paragraph{External validity} 
Our results might not generalize to 
 other instances outside of the studied cases.  To mitigate this risk, we have used a broad and rich 
 dataset~\cite{msr17challenge} in our analysis, comprising 1,359 popular projects.

 Other concerns of the study include the possibility that the social factors
 have changed significantly in the past three years, the collapsing of a
 commit's build success to a single successful build and unsuccessful build
 distorted the results, and the possibility that unsuccessful builds were due to
 incorrect test cases and not low quality contributions. Also, the social factors used
 in this study may not apply to closed source applications, and the factors may
 only capture a developer's experience with open source projects. Future work 
 will be required to investigate the influence of these threats.

>>>>

%\paragraph{Internal validity}
We use Weka, a well known machine-learning toolkit,
to analyze our data.
Like all tools, Weka may contain errors and/or bugs. 
Nonetheless, it is a well-known used, open source tool, and as such is likely
to be of relatively high quality, mitigating threats to internal validity. 
We have made our scripts, which analyzed the datasets and
obtained social data publicly available\footnote{https://goo.gl/CqTX44}, for
extension and reproducibility.
We mitigate the risk that our results fail to 
%\paragraph{External validity} 
generalize externally by studying a broad and rich 
 dataset~\cite{msr17challenge} comprising 1,359 popular projects.
Similarly, the social factors we study may not apply to closed-source
applications; however, open-source ecosystems are intellectually
valuable sources of study on their own. 
%
 Other concerns include the possibility that social factors
 have changed significantly in the past three years, that unsuccessful
 builds are due to
 incorrect test cases (rather than low quality contributions), and that
 information is lost in collapsing commits' multiple builds. We believe these
 are similarly mitigated by a large and varied dataset, but leave investigation
 of the effects of these decisions to future work.
